The effects of priming in human computation

### 2014-05-11 docs/publications/2014.05.9_pnas/figs.tex
changes to manuscript and specificity computation

\begin{document}
\begin{table}[t]
\centering
	\begin{tabular}{ l  l  l }
		\hline                       
		Treatment & Funder$^a$ & Priming Image Set	\\ 
		\hline                       
		$\textsc{ambg}$ & None & Ambiguous\\
		$\textsc{cult}_{img}$ & None & Cultural\\
		$\textsc{cult}_{fund}$ & Cultural & Cultural\\
		$\textsc{cult}_{fund,img}$ & Cultural & Cultural\\
		$\textsc{ingr}_{img}$ & None & Ingredients\\
		$\textsc{ingr}_{fund}$ & Nutritional & Ingredients\\
		$\textsc{ingr}_{fund, img}$ & Nutritional & Ingredients\\
		\hline  
	\end{tabular}

@@

	\caption{Experimental treatments.  Workers were uniformly randomly
		assigned to one of the treatments listed above.  The full funder 
		names used were ``The Glodal Foundation
		for Cultural Recognition'' and ``The National Foundation for 
		Nutritional Awareness''.  The ambiguous, cultural, and ingredients 
		priming images used are shown in \textbf{Figs. B}, \textbf{C}, and 
		\textbf{D}.}
	\label{table:1}
\end{table}

\begin{figure}
	\includegraphics{figs/f1-thetas.pdf}
	\caption{ $F_1$ score and $\theta_\text{NB}$ for the various 
priming treatments, as measured using a Naive Bayes classifier. Each panel 
presents classifier performance results that indicate the difference in
priming between a basis 
treatment, indicated in the inset, and the other treatments, indicated on the
abscissa. }
\end{figure}

\begin{figure}
	\includegraphics{figs/longitudinalF1scores-t1-t2.pdf}
	\caption{ $F_1$ score and $\theta_\text{NB}$ for the classification of 
	$\textsc{cult}_{img}$ and $\textsc{ingr}_{img}$ using a Naive Bayes 
	classifier.  The classifier is provided only the labels attributed to
	particular images as indicated on the abscissa.}
\end{figure}

\begin{figure}
	\includegraphics{figs/orientationVsTreatment.pdf}
	\caption{Percent label composition (culture- vs food-oriented labels) for 
		various images and treatments.  Panel A shows the composition of 
		labels, aggregated over all treatments, as a function of test image.
		Panel B shows the composition of labels, aggregated over all images, as
		a function of treatment.  Panel C shows the composition of labels 
		attributed to the first test image by various treatments.}
\end{figure}

\begin{figure}
	\includegraphics{figs/excessCultureVsTreatment-t1.pdf}
	\caption{Excess culture-oriented label composition in the labels provided
		by $\textsc{cult}_{img}$ as compared to $\textsc{ambg}$, for various
		test images (see \textbf{Eq. 1} for calculation).
	}
\end{figure}

\begin{figure}
	\includegraphics{figs/specificity-allImages.pdf}
	\caption{Relative specificity of various treatments.
		Each panel shows the comparison between a basis treatment (inset) and 
		target treatments (abscissa).
		Bar heights indicate relative specificity of the target 
		treatment compared to the basis (a positive quantity means the target 
		is more specific), and are normalized to units of standard 
		deviations of the null comparison.  Dotted horizontal lines indicate
		the 95\% confidence interval for the null comparison, which necessarily
		has zero relative specificity (see \textbf{Methods} 
		for an explanation of the null comparison).  Panels D, E, and F 
		represent relative specificity calculated using only culture-oriented
		labels, while panels G, H, and I using only food-oriented labels.
		Labels that are both culture- and food-oriented are excluded from the
		calculations for panels D through I.
		}
\end{figure}

\begin{figure}
	\includegraphics{figs/specificity-test0.pdf}
	\caption{Relative specificity of various treatments, for labels attributed
		to the first test image.
		Each panel shows the comparison between a basis treatment (inset) and 
		target treatments (abscissa).
		Bar heights indicate relative specificity of the target 
		treatment compared to the basis (a positive quantity means the target 
		is more specific), and are normalized to units of standard 
		deviations of the null comparison.  Dotted horizontal lines indicate
		the 95\% confidence interval for the null comparison, which necessarily
		has zero relative specificity (see \textbf{Methods} 
		for an explanation of the null comparison).  Panels D, E, and F 
		represent relative specificity calculated using only culture-oriented
		labels, while panels G, H, and I using only food-oriented labels.
		Labels that are both culture- and food-oriented are excluded from the
		calculations for panels D through I.
		}
	\end{figure}

>>>>

\begin{document}
\begin{table}[t]
\centering
	\begin{tabular}{ l  l  l }
		\hline                       
		Treatment & Funder & Priming Image Set	\\ 
		\hline                       
		$\textsc{ambg}$ & None & Ambiguous\\
		$\textsc{cult}_{img}$ & None & Cultural\\
		$\textsc{cult}_{fund}$ & Cultural & Cultural\\
		$\textsc{cult}_{fund,img}$ & Cultural & Cultural\\
		$\textsc{ingr}_{img}$ & None & Ingredients\\
		$\textsc{ingr}_{fund}$ & Nutritional & Ingredients\\
		$\textsc{ingr}_{fund, img}$ & Nutritional & Ingredients\\
		\hline  
	\end{tabular}

@@

	\caption{Workers were uniformly randomly
		assigned to one of the treatments listed above.}
	\label{table:1}
\end{table}

\begin{figure}
	\includegraphics[scale=1.00]{../figs/taskImages/testImages.png}
	\caption{Testing image set. These images were presented to all workers in 
		the order shown after the priming set of images.}
\end{figure}

\begin{figure}
	\includegraphics[scale=1.00]{../figs/taskImages/ambiguous.png}
	\caption{ Ambiguous image set. These images were presented to workers from 
		certain treatements (see \textbf{Table 1}) in the order shown.}
\end{figure}

\begin{figure}
	\includegraphics[scale=1.00]{../figs/taskImages/cultural.png}
	\caption{Cultural image set. These images were presented to workers from 
		certain treatements (see \textbf{Table 1}) in the order shown.}
\end{figure}

\begin{figure}
	\includegraphics[scale=1.00]{../figs/taskImages/ingredients.png}
	\caption{ Ingredients image set. These images were presented to workers 
		from certain treatements (see \textbf{Table 1}) in the order shown.}
\end{figure}

\begin{figure}
	\includegraphics{../figs/f1-thetas.pdf}
	\caption{ $F_1$ score and $\theta_\text{NB}$ for the various 
priming treatments, as measured using a Naive Bayes classifier. Each panel 
presents classifier performance results that indicate the difference in
priming between a basis 
treatment, indicated in the inset, and the other treatments, indicated on the
abscissa. }
\end{figure}

\begin{figure}
	\includegraphics{../figs/longitudinalF1scores-t1-t2.pdf}
	\caption{ $F_1$ score and $\theta_\text{NB}$ for the classification of 
	$\textsc{cult}_{img}$ and $\textsc{ingr}_{img}$ using a Naive Bayes 
	classifier.  The classifier is provided only the labels attributed to
	particular images as indicated on the abscissa.}
\end{figure}

\begin{figure}
	\includegraphics{../figs/orientationVsTreatment.pdf}
	\caption{Percent label composition (culture- vs food-oriented labels) for 
		various images and treatments.  Panel A shows the composition of 
		labels, aggregated over all treatments, as a function of test image.
		Panel B shows the composition of labels, aggregated over all images, as
		a function of treatment.  Panel C shows the composition of labels 
		attributed to the first test image by various treatments.}
\end{figure}

\begin{figure}
	\includegraphics{../figs/excessCultureVsTreatment-t1.pdf}
	\caption{Excess culture-oriented label composition in the labels provided
		by $\textsc{cult}_{img}$ as compared to $\textsc{ambg}$, for various
		test images (see \textbf{Eq. 1} for calculation).
	}
\end{figure}

\begin{figure}
	\includegraphics{../figs/specificity-allImages.pdf}
	\caption{Relative specificity of various treatments.
		Each panel shows the comparison between a basis treatment (inset) and 
		target treatments (abscissa).
		Bar heights indicate relative specificity of the target 
		treatment compared to the basis (a positive quantity means the target 
		is more specific), and are normalized to units of standard 
		deviations of the null comparison.  Dotted horizontal lines indicate
		the 95\% confidence interval for the null comparison, which necessarily
		has zero relative specificity (see \textbf{Methods} 
		for an explanation of the null comparison).  Panels D, E, and F 
		represent relative specificity calculated using only culture-oriented
		labels, while panels G, H, and I using only food-oriented labels.
		Labels that are both culture- and food-oriented are excluded from the
		calculations for panels D through I.
		}
\end{figure}

\begin{figure}
	\includegraphics{../figs/specificity-test0.pdf}
	\caption{Relative specificity of various treatments, for labels attributed
		to the first test image.
		Each panel shows the comparison between a basis treatment (inset) and 
		target treatments (abscissa).
		Bar heights indicate relative specificity of the target 
		treatment compared to the basis (a positive quantity means the target 
		is more specific), and are normalized to units of standard 
		deviations of the null comparison.  Dotted horizontal lines indicate
		the 95\% confidence interval for the null comparison, which necessarily
		has zero relative specificity (see \textbf{Methods} 
		for an explanation of the null comparison).  Panels D, E, and F 
		represent relative specificity calculated using only culture-oriented
		labels, while panels G, H, and I using only food-oriented labels.
		Labels that are both culture- and food-oriented are excluded from the
		calculations for panels D through I.
		}
	\end{figure}

### 2014-05-11 docs/publications/2014.05.9_pnas/pnas2.tex
changes to manuscript and specificity computation

\subsection{Experimental Setup}
We test hysteresis by presenting AMT workers with
five images that depict meals with strong cultural overtones 
(see \textbf{Fig. A}), and ask them to
label each image with descriptive words.  Before presenting test images,
we expose the workers to different priming treatments.  We observe how priming
treatments effect the workers' subsequent choice of labels, by looking at 
how specific the labels are, and how often workers make 
cultural references.

We employ two priming modalities in this study.  
In the first modality, which we call \textit{in-task priming}, workers are 
shown one of three sets of priming images.  The \textit{cultural}
image set, \textbf{Fig. B}, shows images chosen for their clear depiction of an
iconic cultural scene.  The \textit{ingredients} image set, \textbf{Fig. C}, 
shows separated food ingredients, as opposed to the prepared meals shown in 
the test set, and avoids strong cultural signal.  The \textit{ambiguous} 
image set contains images of prepared meals (\textbf{Fig D}), and is most 
similar to the test set, but there are no prominent traces of cultural 
reference.  These images are shown right
before the test images, and they must be labeled in the same way.  From the 
workers' view-point there is no distinction between the priming and test 
images.

The second priming modality, which we call \textit{framing}, consists of
presenting the workers with the name of a (fictitious) research funder before
presenting any images to be labeled.  Workers are shown either the funder 
name  
``The National Foundation for Nutritional Awarenes'' or ``The Global
Foundation for Cultural Recognition'', or else they are shown no name.  These 
names were chosen to signal interest, on the part of the requester, in the
cultural or food-related aspects of the images.

We also test interaction effects between framing and in-task priming.  The
various treatments are listed in \textbf{Table 1}.

@@

We can compare the bulk specificity of two treatments by taking a subsample
of workers from each, and the labels of the workers in one
subsample to each of those in the other.  In drawing this comparison, we only 
compare labels that were attributed to the same image.  Thus the relative 
specificity of two treatments can then be computed as:
\begin{align}
	S(\textsc{x},\textsc{y}) = 
		\sum_{i=1}^5 \; 
		\sum_{\ell\in \mathcal{L}(\textsc{x},i)} \;
		\sum_{m\in \mathcal{L}
		(\textsc{y},i)} \left(\mathbf{1}[\ell > m] 
		- \mathbf{1}[m>\ell]\right),
\end{align}
Where \textsc{x} and \textsc{y} are treatment subsamples,
$\mathcal{L}(\textsc{x},i)$ is the set of all labels produced by workers in 
$\textsc{x}$ for test image $i$, and $\mathbf{1}[\ell > m]$ evaluates to 1 if 
$\ell$ is more specific than $m$, and 0 otherwise.  \textbf{Figure 9} 
exhibits the results.

@@

@@

\paragraph{Figure A.}
	Testing image set. These images were presented to all workers in the order 
	shown after the priming set of images.

\paragraph{Figure B.}
	Ambiguous image set. These images were presented to workers from certain
	treatements (see \textbf{Table 1}) in the order shown.

\paragraph{Figure C.}
	Cultural image set. These images were presented to workers from certain
	treatements (see \textbf{Table 1}) in the order shown.

\paragraph{Figure D.}
	Ingredients image set. These images were presented to workers from certain
	treatements (see \textbf{Table 1}) in the order shown.

>>>>

\subsection*{Experimental Setup}
AMT workers are randomly assigned to one of seven treatments 
(see \textbf{Table 1}).  After brief instructions, workers are either
shown a credit for the research funder, which can be either 
``The Global foundation for Cultural Recognition'', or 
``The National Foundation for Nutritional Awareness'', or else they are 
immediately presented with a prior image set.

The prior and posterior images sets both consist of five images. Each image 
must be assigned labelled five labels.  For the posterior image set we chose 
images that contain prepared meals and feature a prominent, iconic culture 
(see \textbf{Fig. 1}).  These images provide a wide array of possible labels, 
may focus on food, culture or both.

One of the prior image sets, which we call \textit{ambiguous}, was chosen to
be most similar to the posterior image set, and contains images of prepared
meals, but whose cultural features are less prominent (see \textbf{Fig. 2}).  
The \textit{cultural} set features iconic cultural scenes, and no food at all
(see \textbf{Fig. 3}).  Finally, images from
the \textit{ingredients} image set depict separated ingredients, having no
prominent cultural aspects (see \textbf{Fig. 4}).  \textbf{Table 1} shows the 
combinations of framing and in task priming that we used for each 
experimental treatment.  See the \textbf{Materials and Methods} section for
further details.

@@

We can compare the bulk specificity of two treatments by taking a subsample
of workers from each, and the labels of the workers in one
subsample to each of those in the other.  In drawing this comparison, we only 
compare labels that were attributed to the same image.  Thus the relative 
specificity of two treatments can then be computed as:

We can compare the specificity of two workers by comparing, for each image,
labels given by one worker with those of the other.  Thus, we define the the
relative specificity of worker $u$ to worker $v$ to be $s(u,v)$:

\begin{align}
	s(u,v) = \sum_{i=1}^5 \;
	\sum_{\ell \in u(i) } \;
	\sum_{m \in v(i)} 
	\left(\mathbf{1}[\ell > m] - \mathbf{1}[m>\ell]\right),
	\label{eq:worker-specificity}
\end{align}

We can then calculate the relative specificity of two treatments to be the
average relative specificity of workers drawn uniformly from the treatments.

\begin{align}
	S(U,V) = 
		\frac{1}{|U \times V|}
		\sum_{(u,v) \; \in \; U \times V} \;
		s(u,v)
		\label{eq:specificity}
\end{align}

Where \textsc{x} and \textsc{y} are treatment subsamples,
$\mathcal{L}(\textsc{x},i)$ is the set of all labels produced by workers in 
$\textsc{x}$ for test image $i$, and $\mathbf{1}[\ell > m]$ evaluates to 1 if 
$\ell$ is more specific than $m$, and 0 otherwise.  \textbf{Figure 9} 
exhibits the results.

@@

\subsection*{Materials and Methods}

\textbf{AMT Tasks.} The task desicribed in the \textbf{Experimental Setup}
section was served to 900 workers, who were uniformly randomly assigned to
treatments.  All treatments had at least 134 task completions.  Workers were
only allowed to participate once and could not see the prior or posterior 
images when previewing the task.

\textbf{Building the ontology of terms.}  The ontology was built by hand, 
starting from the corpus of labels. Labels occuring only once were discarded.  
We created the 
root classes \texttt{activity}, \texttt{adjective}, \texttt{culture}, 
\texttt{food}, and \texttt{thing}. \texttt{culture} and \texttt{food} were 
given top-level status because they were prominently represented in the corpus.
Some labels descend from both \texttt{food} and \texttt{cultural}  
(e.g. \texttt{naan}), but there were also \texttt{food} labels that had no
obvious cultural association (e.g. \texttt{bread}). Whenever one label 
could be regarded as a more specific case of another, they were given a 
child-parent relationship. In some cases missing abstract labels were added to 
the ontology.  Labels which were roughly synonymous were treated as identical,
and misspellings were handled the same way.

\textbf{Assessing relative specificity.}
We used \textbf{Eq.~\ref{eq:specificity}} to compute the relative specificity
of two treatments.  To analyze this similarity measure statistically
we define the specificity of a worker $u$ relative to a 
\textit{basis treatment} $V$ as $S_V(u)$:
\begin{align}
S_V(u) = \frac{1}{|V|} \sum_{v \in V} s(u,v),
\end{align}
And rewrite the relative specificity of $U$ and $V$ as the expected value of
$S_V(u)$ for workers in $U$:
\begin{align}
	S(U,V) &= E\{S_V(u)\}, \\
	\text{with} \quad\quad \text{Var}\{S(U,V)\} 
		&= \frac{\text{Var}\{S_V(u)\}}{|U|}.
\end{align}
To decide if $U$ is significantly more (less) specific than $V$, we do
a null comparison of $V$ to itself: $S(V,V)$.  This value is in principle zero,
but the comparison yields $\text{Var}\{S(V,V)\}$ which we use to state and 
test the null hypothesis that $U$ and $V$ are equally specific:
\begin{align}
	\mathbf{H_0}: \quad S(U,V)-S(V,V)=0
\end{align}
Note that since $S(V,V)=0$, $\mathbf{H_0}$ essentially states that $S(U,V)=0$,
however, it is more stringent since we consider variance due to sampling both
$U$ and $V$:
\begin{align}
\text{Var}\{S(U,V) - S(V,V)\} &= \text{Var}\{S(U,V)\} + \text{Var}\{S(V,V)\}\\
						&> \text{Var}\{S(U,V)\}
\end{align}
Therefore, we find $U$ to be significantly more (less) specific than $V$ when:
\begin{align}
z = \frac{S(U,V)}{ \sqrt{ \text{Var}\{S(U,V)\} + \text{Var}\{S(V,V)\} }} 
	> 1.96.
\end{align}

Due to 
computational intensity, we randomly subsampled 65 workers from each treatment.
To compute the relative food- or culture-specificity, we alter the calculation
in \textbf{Eq.~\ref{eq:worker-specificity}} by only including labels 
respectively of food- or culture-orientation, while excluding all labels that
aro both food- and culture-oriented.

@@

\paragraph{Figure 1.}
	Testing image set. These images were presented to all workers in the order 
	shown after the priming set of images.

\paragraph{Figure 2.}
	Ambiguous image set. These images were presented to workers from certain
	treatements (see \textbf{Table 1}) in the order shown.

\paragraph{Figure 3.}
	Cultural image set. These images were presented to workers from certain
	treatements (see \textbf{Table 1}) in the order shown.

\paragraph{Figure 4.}
	Ingredients image set. These images were presented to workers from certain
	treatements (see \textbf{Table 1}) in the order shown.
